### 2015-01-16 publishing/plos_template.tex
figure and caption added for oxygen data

>>>>

\begin{figure}
\includegraphics[scale=0.3]{../presentation-figures/6-well-plot.png} % remove for manuscript submission
\includegraphics[scale=0.3]{../presentation-figures/24-well-plot.png} % remove for manuscript submission
\caption{
{\bf Oxygen Characterization.}  Time course data of oxygen being evacuated from the culture area as 0\% oxygen gas is perfused through the device. Each 6 well row of the plate can be controlled independently.  
}
\label{Figure_label}
\end{figure}
